|

### 2021-08-11 prova_knit_finale.Rmd
typo

Assume that $\P_{t-1}(dx_{t-1}\mid Y_{1:t-1}=y_{1:t-1})=\N(m_{t-1},C_{t-1}).$
Then, using the transition equation of the latent variable, 
by the linearity of the Gaussian distribution, we have that the predictive distribution is 
\begin{equation}
\P_{t-1}(dx_{t}\mid Y_{1:t-1}=y_{1:t-1})=\N(A_tm_{t-1},A_tC_{t-1}A_t'+\Sigma_t).
\end{equation}
Letting $R_T=A_tC_{t-1}A_t'+\Sigma_t,$ and applying lemma \ref{kalman-filter}, it follows that the filtering distribution is 
\begin{align*}
  \P_{t}(X_t\in dx_{t}\mid Y_{1:t-1}&=y_{1:t-1})=\N(m_t,C_t), \text{ where} \\ C_t&=R_t[I_{d_x} - B_t'(B_tR_tB_t'+\Lambda_t)^{-1} B_tR_t] \\
  m_t &= [I_{d_x} - R_tB_t'(B_tR_tB_t'+\Lambda_t)^{-1} B_t]A_tm_{t-1}+R_tB_t'(B_tR_tB_t'+\Lambda_t)^{-1}y_t.
\end{align*}

>>>>

Assume that $\P_{t-1}(dx_{t-1}\mid Y_{1:t-1}=y_{1:t-1})=\N(m_{t-1},C_{t-1}).$
Then, using the transition equation of the latent variable, 
by the linearity of the Gaussian distribution, we have that the predictive distribution is 
\begin{equation}
\P_{t-1}(dx_{t}\mid Y_{1:t-1}=y_{1:t-1})=\N(A_tm_{t-1},A_tC_{t-1}A_t'+\Sigma_t).
\end{equation}
Letting $R_T=A_tC_{t-1}A_t'+\Sigma_t,$ and applying lemma \ref{kalman-filter}, it follows that the filtering distribution is 
\begin{align*}
  \P_{t}(X_t\in dx_{t}\mid Y_{1:t}&=y_{1:t})=\N(m_t,C_t), \text{ where} \\ C_t&=R_t[I_{d_x} - B_t'(B_tR_tB_t'+\Lambda_t)^{-1} B_tR_t] \\
  m_t &= [I_{d_x} - R_tB_t'(B_tR_tB_t'+\Lambda_t)^{-1} B_t]A_tm_{t-1}+R_tB_t'(B_tR_tB_t'+\Lambda_t)^{-1}y_t.
\end{align*}
